Scheduling and Vectorization for MPC

### 2022-03-22 overleaf/paper_SIMD.tex
Add write-up for 3-address CFG conversion

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}: TODO
  \item
        \textbf{SSA conversion}:
        Convert the 3-address CFG to SSA with Cytron's algorithm.
\end{enumerate}

>>>>

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}:
        TODO: Is this a good amount of detail?

        Convert the restricted-syntax AST to a three-address control-flow graph.
        To do this, first,
        add an empty basic block to the CFG and mark it as current.
        Next, for each statement in the restricted AST's function body,
        process the statement.
        Statements can either be for-loops, if-statements, or assignments.
        Rules for processing each kind of statement are given below:
        \begin{enumerate}
          \item
                \textbf{For-loops}:
                Create new basic blocks for
                the loop condition
                (the condition block),
                the loop body
                (the body block),
                and the code after the loop
                (the after-block).
                Insert a jump from the end of the current block to the condition block.
                Then, mark the condition block as the current block.
                Insert a for-instruction at the end of the current block with the loop counter variable and bounds from the AST.
                Next, add an edge from the current block to the after-block labeled ``FALSE'' and
                an edge from the current block to the
                body block labeled ``TRUE''.
                Then, set the body block to be the current block
                and process all statements in the AST's loop body.
                Finally, insert a jump to the condition block and set the after-block as current.
          \item
                \textbf{If-statements}:
                Create new basic blocks for
                the ``then'' statements of the if-statement
                (the then-block),
                the ``else'' statements of the if-statement
                (the else-block),
                and the code after the if-statement
                (the after-block).
                At the end of the current block,
                insert a conditional jump to the then-block or else-block
                depending on the if-statement condition in the AST.
                Next,
                mark the then-block as current,
                process all then-statements,
                and add a jump to the after-block.
                Similarly,
                mark the else-block as current,
                process all else-statements,
                and add a jump to the after-block.
                Finally, set the after-block to be the current block,
                and give it a ``merge condition'' property equal to the condition of the if-statement.
          \item
                \textbf{Assignments}:
                In the restricted-syntax AST,
                the left-hand side of assignments
                can be a variable or an array subscript.
                If it is an array subscript such as \texttt{A[i] = x},
                change the statement to \texttt{A = Update(A, i, x)}.
                If the statement is not already three-address code,
                for each sub-expression in the right-hand side of the assignment,
                insert an assignment to a temporary variable.
        \end{enumerate}
  \item
        \textbf{SSA conversion}:
        Convert the 3-address CFG to SSA with Cytron's algorithm.
\end{enumerate}
